Using Metric Space Indexing for Complete and Efficient Record Linkage

### 2017-11-21 paper.tex
Update on Overleaf.

\begin{figure}
\begin{verbatim}
Figure 3 will be a table of Comparisons, F1, precision recall and pairs stuff.
12 ROWS ISH
\end{verbatim}
\caption{Linkage Quality using Brute Force linking on the Cora data set\label{comparison-of-results}}
\end{figure}

\Cref{cora-traditional-prf} plots the linkage quality values obtained by running traditional blocking based linkage at a threshold level of 70. Here, we see that high precision values are possible using blocking based linkage, however the recall (and as a result the F-measure) is poor in comparison to brute-force.

\begin{figure}
\includegraphics[width=\textwidth]{figures/plotFixedThresholdTraditional1_--_Cora_-_TradBlocking_-_70}
\caption{Linkage Quality using traditional blocking on the Cora data set\label{cora-traditional-prf}}
\end{figure}

\subsection{M-Tree}

M-Tree is a complete method that avoids brute-force search.
In addition, it does not require any additional engineering work, it works with any distance metric.

\begin{figure}
\includegraphics[width=\textwidth]{figures/plotBQ_--_Cora_-_Brute_Force}
\caption{Block Quality - Brute Force\label{cora-block-quality-brute}}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{figures/plotBQ_--_Cora_-_MTree}
\caption{Block Quality - M-Tree\label{cora-block-quality-mtree}}
\end{figure}

\subsection{Historical Demography results}
\begin{itemize}
\item Fig X -1 Repeat of figure 2 with precision recall comparisons etc.
\item Fig X - Kilmarnock M tree plot Precision,recall and F
\item Fig X + 1 - Skye M tree plot Precision,recall and F
\item Fig X + 2 - Mtree F measure and a bunch LSH F measures.
\end{itemize}

>>>>

\begin{figure}
\begin{verbatim}
This will be a table of Comparisons, F1, precision recall and pairs stuff.
12 ROWS ISH
\end{verbatim}
\caption{Linkage Quality on the Cora data set\label{comparison-of-results}}
\end{figure}

\subsection{Historical Demography results}

\begin{figure}
\begin{verbatim}
This will be a table of Comparisons, F1, precision recall and pairs stuff for Skye/Kilmarnock
12 ROWS ISH
\end{verbatim}
\caption{Linkage Quality on the Cora data set\label{comparison-of-results}}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{figures/plotBQ_--_Cora_-_Brute_Force}
\caption{Will be Linkage quality with M-Tree Skye\label{cora-block-quality-brute}}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{figures/plotBQ_--_Cora_-_MTree}
\caption{Will be Linkage quality with M-Tree Kilmarnock\label{cora-block-quality-mtree}}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{figures/plotBQ_--_Cora_-_MTree}
\caption{Will be Mtree F measure and a bunch LSH F measures\label{cora-block-quality-mtree}}
\end{figure}
